Transmembrane helices are also an overlooked source of major histocompatibility complex class II epitopes and evolutionary more conserved than expected by chance

### 2020-04-07 article.tex
EOD

For MHC-1, it was found that epitopes derived from transmembrane helices (TMHs)
are over-presented by all human leukocyte antigen (HLA)-A and most HLA-B super 
types [\cite{bianchi2017transmembrane}]. One explanation is that the 
presentation of especially TMHs may have an evolutionary advantage for 
the (human) host. The argumentation for this is that the TMHs are more 
conserved due to the functional requirement of being able to span a lipid 
bilayer. Additionally, there are limited escape mutations possible for the 
pathogen, as many will result in a non-functional TMH. 
However, that argumentation can also be countered as there are limited unique 
polypeptide fragments and TMHs are a conserved throughout all species, it is 
likelier that host and pathogen share the same unique epitope sequences, 
resulting in the pathogen avoiding detection due to the negative T-cell 
selection process in the thymus.

>>>>

For MHC-1, it was found that epitopes derived from transmembrane helices (TMHs)
are over-presented by all human leukocyte antigen (HLA)-A and most HLA-B super 
types [\cite{bianchi2017transmembrane}]. One explanation is that the 
presentation of especially TMHs may have an evolutionary advantage for 
the (human) host. The argumentation for this is that the TMHs are more 
conserved due to the functional requirement of being able to span a lipid 
bilayer. Additionally, there are limited escape mutations possible for the 
pathogen, as many will result in a non-functional TMH.

However, that argumentation can also be countered as there are limited unique 
polypeptide fragments and TMHs are a conserved throughout all species, it is 
likelier that host and pathogen share the same unique epitope sequences, 
resulting in the pathogen avoiding detection due to the negative T-cell 
selection process in the thymus \richel{Frans, jij beweerde dat bacterien
en mensen compleet verschillende TMH sequenties hebben. Als ik dat goed
onthouden hebt, klopt deze paragraaf dus niet}
